### 2017-04-09 sections/conclusion.tex
Update on Overleaf.

The goal of this paper is to present the use of SVD decomposition in compression of results from the Finite element method. Theoretical properties of SVD decomposition have been described, implementation details of compression algorithm have been provided, and results of its application on real data have been presented.

The implemented algorithm is able to compress arbitrary data using the low-rank approximation matrices. If the maximum allowed error was set to $10^{-5}$ then the compression ratio was at least 10\% for all tested results. In many cases compression ratio can be even much lower -- bellow 1\% of the original size. The important property of compression algorithm is the fact that the approximation error can be set in advance and there is a guarantee that it will not be exceeded.

@@

Other complication is the necessity to use special format to store compressed data in the form of SVD decomposition and the post-processor must be updated to use this new format. Post-processor must perform matrix multiplication to get the original results. However, in usual case the data for one analysis step are needed at a time, i.e. only a partial multiplication of a single row is enough.

>>>>

The goal of this paper is to present the use of SVD decomposition in compression of results from the Finite element method. Implementation details of compression algorithm have been provided, and results of its application on real data have been presented. The implemented algorithm is able to compress arbitrary data using low-rank approximation matrices. If the maximum allowed error was set to $10^{-5}$ then the compression ratio was at least 10\% for all tested results. In many cases compression ratio can be even much lower -- bellow 1\% of the original size. The important property of compression algorithm is the fact that the approximation error can be set in advance and there is a guarantee that it will not be exceeded.

@@

Other complication is the necessity to use special format to store compressed data in the form of SVD decomposition and the post-processor must be updated to use this new format. Post-processor must perform matrix multiplication to get the original results. However, in usual case the data for one analysis step are needed at a time, i.e. only a partial multiplication of a single row is enough. Detailed description of a post-processor implementation is beyond the scope of this paper.

### 2017-04-09 sections/math.tex
Update on Overleaf.

SVD can be seen as a method for transforming correlated variables into a set of uncorrelated ones that better expose the various relationships among the original data items. At the same time, SVD is a method for identifying and ordering the dimensions along which data points exhibit the most variation. Once we have identified where the most variation is, it is possible to find the best approximation of the original data points using fewer dimensions. Hence, SVD can be seen as a method for data reduction/compression.

@@

Low-rank approximation matrix method that is described in this paper is a lossless compression technique. Several error metrics are used to control the quality of results \cite{SairaBanu2015}.

@@

\noindent
where $X_{min}$ and $X_{max}$ are elements of input matrix $\mtrx{A}$ with minimum and maximum value, respectively.

@@

PSNR is most commonly used to measure the quality of reconstruction of lossy compression methods (e.g. image compression). The signal in this case is the original data, and the noise is the error introduced by compression. When comparing compression methods, PSNR is an approximation to human perception of reconstruction quality. PSNR is usually expressed in terms of the logarithmic decibel scale (dB).

>>>>

SVD can be seen as a method for transforming correlated variables into a set of uncorrelated ones. At the same time, SVD is a method for identifying and ordering the dimensions along which data points show the most variation. Once we have identified where the most variation is, it is possible to find the best approximation of the original data points using fewer dimensions. Hence, SVD can be seen as a method for data reduction/compression.

@@

Low-rank approximation matrix method that is described in this paper is a lossy compression technique. Several error metrics are used to control the quality of results \cite{SairaBanu2015}.

@@

\noindent
where $X_{min}$ and $X_{max}$ are elements of input matrix $\mtrx{A}$ with minimum and maximum value, respectively. Being able to compare datasets with different scales this is the main parameter that is used to control quality of compression in the algorithm presented in this paper.

@@

PSNR is most commonly used to measure the quality of reconstruction of lossy compression methods (e.g. image compression). The signal in this case is the original data, and the noise is the error introduced by compression. PSNR is an approximation to human perception of reconstruction quality. This metric is not so important in area of FEM analyses where the human perception of visualizations is not as important as the exact mathematical accuracy of approximations. The reason to include PSNR in results is in particular to allow comparison with other image-related compression methods. PSNR is usually expressed in terms of the logarithmic decibel scale (dB).
